Revision Plan for SIGCOMM'24 Paper \#293

### 2024-05-20 revision_plan.tex
grammly

\noindent\textcolor{blue}{\textbf{Response A.1:}
Thanks for the reviewer’s comments. 
Actually, PPT uses eight strict priorities in the switch.
To prevent HCP traffic harmed by LCP, priorities 0$\sim$3 are used to transmit HCP packets and priorities 4$\sim$7 are used to transmit LCP packets.
Therefore, the \emph{high-priority} and \emph{low-priority} mentioned in p.6 as well as p.9 refer to priorities 0$\sim$3 and priorities 4$\sim$7 in the switch, respectively.
To avoid ambiguity for the reader, we will include footnotes in Section 3.2 for explanation.
}

@@

\noindent\textcolor{blue}{\textbf{Response A.2:}
Thanks for the reviewer’s comments. 
Although very sorry, the reviewer seems to have misinterpreted  PPT's strategy.
At the beginning of Section 3, we mentioned that "LCP sends opportunistic packets from the tail end".
Therefore, both HCP and LCP send data in same flow.
However, many of the review's comments were based on LCP and HCP transmitting data from different flows, which made them difficult for us to answer.
}

@@

\noindent\textcolor{blue}{\textbf{Response B.1:}
Thanks for the reviewer’s comments. 
Since the NIC rate can be read via system call and the datacenter network topology is relatively fixed, we assume that the RTT is known a priori.
By NIC rate times RTT, we assume that the host knows the BDP by advance.
}

@@

\noindent\textcolor{blue}{\textbf{Response B.2:}
Thanks for the reviewer’s comments. 
During the process of congestion subsiding, the switch queue length is reducing, the percentage of ECN marked packets for this long flow is decreasing, as well as the value of $\alpha$.
As the congestion subsides completely, the proportion of ECN-marked packets should be 0.
PPT initializes LCP for the long flow whenever $\alpha$ takes the minimum value.
At this point, $\alpha$ must be less than 0.5, which makes this large flow utilize the spare bandwidth.
}

@@

\noindent\textcolor{blue}{\textbf{Response B.4:}
Thanks for the reviewer’s comments. 
We will add a new simulation experiment with topology consists of 144 servers, 9 leaf switches and 4 spine switches, with the host and core links operated at 400 and 1000Gbps, respectively.
We will plot the results in the appendix.
}

@@

\noindent\textcolor{blue}{\textbf{Response B.5:}
Thanks for the reviewer’s comments. 
Actually, we measure the kernel space CPU overhead of PPT and DCTCP in the our testbed.
We plot the results in Figure 21.
For more details can read Appendix C.1.
}

@@

\noindent\textcolor{blue}{\textbf{Response C.1:}
Thanks for the reviewer’s comments. 
Indeed, in section 2.3 we mention that \emph{DCTCP marks ECN at the switch for arriving packets if queue occupancy exceeds a threshold K, and the sender cuts the window based on the fraction of ECN marked ACKs. So, when there are multiple concurrent flows, DCTCP may mark ECN for packets from many flows, which may cut windows simultaneously, thus causing a sudden drain on the switch buffer and leaving bandwidth underutilized.}
To show this point, We run ns-3 simulations with two senders and one receiver sharing the bottleneck. 
We sample the bottleneck link utilization every 100us for 10ms when DCTCP enters a steady state.
We plot the results in Figure 1 and show that  leaving nearly half of the bandwidth under-utilized.
}

@@

\noindent\textcolor{blue}{\textbf{Response C.2:}
	Thanks for the reviewer’s comments. 
	After careful checking of our data processing code we found that under Datamining workloads, RC3 would result in few flows not completing due to a large number of packet losses.
	Our code incorrectly used the program runtime as the flow completion time when calculating the overall average FCT, resulting in the actual calculated result being larger.
	We will fix the bug and update the correct result.
}

@@

\noindent\textcolor{blue}{\textbf{Response C.3:}
Thanks for the reviewer’s comments. 
Although limiting the RC3 low-priority queue can reduce the LCP from sending too many opportunity packets somehow, the following reasons still lead to low performance.
First, during the slow-start phase of the flow, limiting the buffer LCP could use will leave a large amount of bandwidth underutilized.
Second, RC3 keeps the LCP open instead of intermittent initialization as PPT, which causes more severe congestion during traffic bursts.
Last but not least, RC3 lack of using in-network priority causes small flow packets are queued after LCP packets, increasing small flow latency.
We will add the above analyses to our paper.
}

@@

\noindent\textcolor{blue}{\textbf{Response D.1:}
Thanks for the reviewer’s comments. 
In fact, as we mentioned in Section 6.1.2, Homa-Linux sends BDP-sized unscheduled packets for each arriving flow, and excessive opportunity packets cause heavier congestion in incast scenarios.
Furthermore, Homa-Linux is connectionless, so packet loss recovery is achieved through retransmission after timeout.
Large packet loss in Incast scenarios further impairs its performance.
We will add more detailed analyses in the paper
}

@@

\noindent\textcolor{blue}{\textbf{Response E.1:}
Thanks for the reviewer’s comments. 
In fact, we construct a stricter variant of PPT in our paper that assigns all packets the same priority.
We plot the results in Figure 19.
We find that even under these conditions, PPT still achieves the optimal overall average FCT among NDP, Homa, Aeolus, DCTCP, and RC3.
}

>>>>

\noindent\textcolor{blue}{\textbf{Response A.1:}
Thanks for the reviewer’s comments. 
PPT uses eight strict priorities in the switch.
To prevent HCP traffic harmed by LCP, priorities 0$\sim$3 are used to transmit HCP packets, and priorities 4$\sim$7 are used to transmit LCP packets.
Therefore, the \emph{high-priority} and \emph{low-priority} mentioned in p.6 and p.9 refer to priorities 0$\sim$3 and 4$\sim$7 in the switch, respectively.
To avoid ambiguity, we will include footnotes in Section 3.2 for explanation.
}

@@

\noindent\textcolor{blue}{\textbf{Response A.2:}
Thanks for the reviewer's comments. 
Although very sorry, the reviewer seems to have misinterpreted PPT's strategy.
At the beginning of Section 3, we mentioned that "LCP sends opportunistic packets from the tail end."
Therefore, both HCP and LCP send data in the same flow.
However, many of the review's comments were based on LCP and HCP transmitting data from different flows, which made it difficult for us to answer.
}

@@

\noindent\textcolor{blue}{\textbf{Response B.1:}
Thanks for the reviewer’s comments. 
Since the NIC rate can be read via system call and the datacenter network topology is relatively fixed, we assume the RTT is known a priori.
By NIC rate times RTT, we assume the host knows the BDP in advance.
}

@@

\noindent\textcolor{blue}{\textbf{Response B.2:}
Thanks for the reviewer’s comments. 
During the process of congestion subsiding, the switch queue length is reduced, the percentage of ECN marked packets for this long flow decreases, and the value of $\alpha$.
As the congestion subsides completely, the proportion of ECN-marked packets should be 0.
PPT initializes LCP for the long flow whenever $\alpha$ takes the minimum value.
At this point, $\alpha$ must be less than 0.5, which makes this large flow utilize the spare bandwidth.
}

@@

\noindent\textcolor{blue}{\textbf{Response B.4:}
Thanks for the reviewer’s comments. 
We will add a new simulation experiment with topology consisting of 144 servers, 9 leaf switches, and 4 spine switches, with the host and core links operated at 400 and 1000Gbps, respectively.
We will plot the results in the appendix.
}

@@

\noindent\textcolor{blue}{\textbf{Response B.5:}
Thanks for the reviewer’s comments. 
Actually, we measure the kernel space CPU overhead of PPT and DCTCP in our testbed.
We plot the results in Figure 21.
For more details, please read Appendix C.1.
}

@@

\noindent\textcolor{blue}{\textbf{Response C.1:}
Thanks for the reviewer’s comments. 
Indeed, in section 2.3, we mention that \emph{DCTCP marks ECN at the switch for arriving packets if queue occupancy exceeds a threshold K, and the sender cuts the window based on the fraction of ECN marked ACKs. So, when there are multiple concurrent flows, DCTCP may mark ECN for packets from many flows, which may cut windows simultaneously, thus causing a sudden drain on the switch buffer and leaving bandwidth underutilized.}
To show this point, We run ns-3 simulations with two senders and one receiver sharing the bottleneck. 
We sample the bottleneck link utilization every 100us for 10ms when DCTCP enters a steady state.
We plot the results in Figure 1, showing that nearly half of the bandwidth is underutilized.
}

@@

\noindent\textcolor{blue}{\textbf{Response C.2:}
Thanks for the reviewer’s comments. 
After carefully checking our data processing code, we found that under Datamining workloads, RC3 would result in a few flows not completing due to many packet losses.
Our code incorrectly used the program runtime as the flow completion time when calculating the overall average FCT, resulting in the actual computed result being larger.
We will fix the bug and update the correct result.
}

@@

\noindent\textcolor{blue}{\textbf{Response C.3:}
Thanks for the reviewer's comments. 
Although limiting the RC3 low-priority queue can prevent the LCP from sending too many opportunity packets, the following reasons still lead to low performance.
First, during the slow-start phase of the flow, limiting the buffer LCP could use will leave a large amount of bandwidth underutilized.
Second, RC3 keeps the LCP open instead of intermittent initialization as PPT, which causes more severe congestion during traffic bursts.
Last but not least, RC3's lack of using in-network priority causes small flow packets to be queued after LCP packets, increasing small flow latency.
We will add the above analyses to our paper.
}

@@

\noindent\textcolor{blue}{\textbf{Response D.1:}
Thanks for the reviewer’s comments. 
As mentioned in Section 6.1.2, Homa-Linux sends BDP-sized unscheduled packets for each arriving flow, and excessive opportunity packets cause heavier congestion in incast scenarios.
Furthermore, Homa-Linux is connectionless, so packet loss recovery is achieved through retransmission after timeout.
Large packet loss in Incast scenarios further impairs its performance.
We will add more detailed analyses in the paper.
}

@@

\noindent\textcolor{blue}{\textbf{Response E.1:}
Thanks for the reviewer’s comments. 
In our paper, we construct a stricter variant of PPT that assigns all packets the same priority.
We plot the results in Figure 19.
Even under these conditions, we find that PPT still achieves the optimal overall average FCT among NDP, Homa, Aeolus, DCTCP, and RC3.
}
